---
title: "XGBM_Claims_Severity_Modelling"
output: html_document
---

### Modelling Car Insurance Claims Severity with XGBoost
In this markdown, we want to estimate the severity of a claim using Extreme Gradient Boosting in R.

```{r}
# Load the data
df<-read.csv("C:\\Users\\William\\Documents\\Data Science - ML\\Pricing Project_GLM_vs_GBM\\data.csv")
```

```{r}
# Replace the NS by 0 and filter only on claims greater than 0.
suppressMessages(suppressWarnings(library(dplyr)))
df <- df %>% mutate(ClaimAmount = ifelse(is.na(ClaimAmount), 0, ClaimAmount)) %>% filter(ClaimAmount > 0)

# Train and Test sets
set.seed(564738291)
u <- runif(dim(df)[1], min = 0, max = 1)
df$train <- u < 0.7
df$test <- !(df$train)
```

We use the package {vtreat} to perform a one-hot encoding on the potential predictors.
```{r}
# Applies vtreat to one-hot encode the training and testing data sets
suppressMessages(suppressWarnings(library(vtreat)))
suppressMessages(suppressWarnings(library(dplyr)))

# variable names
# Isolate the outcome from the potential predictors and the Exposure
df_train <- df%>% filter(train == TRUE) %>% select(ClaimAmount, ClaimNb, Exposure,
                                                   Power, CarAge, DriverAge, Brand, Gas, Region, Density)
df_test <- df%>% filter(test == TRUE) %>% select(ClaimAmount, ClaimNb, Exposure,
                                                 Power, CarAge, DriverAge, Brand, Gas, Region, Density)
features <- setdiff(names(df_train), c("ClaimAmount", "Exposure"))
#print(features)

# Create the treatment plan from the training data selecting only the features to be used for the training
treatplan <- vtreat::designTreatmentsZ(df_train, features, verbose = FALSE)
#print(treatplan)

# Get the "clean" variable names from the scoreFrame
new_vars <- treatplan %>%
  magrittr::use_series(scoreFrame) %>%        
  dplyr::filter(code %in% c("clean", "lev")) %>% 
  magrittr::use_series(varName)  

# print only the 10 first encoded variable
print(head(new_vars,10)) 
```

Then we prepare the train and test sets.
```{r}
# Prepare the training data
features_train <- vtreat::prepare(treatplan, df_train, varRestriction = new_vars) %>% as.matrix()
response_train <- df_train$ClaimAmount/df_train$ClaimNb # Need the average severity

# Prepare the test data
features_test <- vtreat::prepare(treatplan, df_test, varRestriction = new_vars) %>% as.matrix()
response_test <- df_test$ClaimAmount/df_train$ClaimNb
#response_test2 <- df_test$ClaimNb

# dimensions of one-hot encoded data
#suppressWarnings(dim(features_train))
#suppressWarnings(dim(features_test))

# Remove the ClaimNb in both sets
features_train <- subset(features_train, select = -ClaimNb)
features_test <- subset(features_test, select = -ClaimNb)
```

### Training a first model
```{r}
# create parameter list
params_list <- list(
  eta = .3,
  max_depth = 5,
  min_child_weight = 2,
  subsample = .8,
  colsample_bytree = .9
)

library(xgboost)
# First model
# Here it incorporates the cross-validation
system.time(xgb.fit.sev <- xgb.cv(
  data = features_train,
  label = response_train, #number claims / exposure for frequency and average claim for severity.
  params = params_list,
  nrounds = 500,# number of trees
  nfold = 5,
  booster = 'gbtree',
  objective = "reg:gamma",  # for severity model
  #eval-metric = "poisson-nloglik", # Negative Log Likelohood, as evaluation metric by default
  tree_method = "hist",
  verbose = 0               # silent,
))

# Check results
#head(xgb.fit.sev$evaluation_log)

# get number of trees that minimize error
xgb.fit.sev$evaluation_log %>%
  dplyr::summarise(
    ntrees.train = which(train_gamma_nloglik_mean == min(train_gamma_nloglik_mean))[1],
    log_lik.train   = min(train_gamma_nloglik_mean),
    ntrees.test  = which(test_gamma_nloglik_mean == min(test_gamma_nloglik_mean))[1],
    log_lik.test   = min(test_gamma_nloglik_mean),
  )
# ntrees.train log_lik.train ntrees.test log_lik.test
# 1          500     7.949184	45	8.675533
```

```{r}
library(ggplot2)
# plot error vs number trees
ggplot2::ggplot(xgb.fit.sev$evaluation_log) +
  geom_line(aes(iter, train_gamma_nloglik_mean), color = "red") +
  geom_line(aes(iter, test_gamma_nloglik_mean), color = "blue") + ggtitle("Neg LogLikelihood Evo")
```

Train and test error are following the same path.

### Run a grid search
An example of grid below that has been run, with 32 parameters.
```{r}
#####################
# Run a grid search #
#####################

# create hyperparameter grid
hyper_grid <- expand.grid(
  eta = c(.01, .05),
  max_depth = c(1, 3),
  min_child_weight = c(1, 3),
  subsample = c(.65, .8),
  colsample_bytree = c(.8, .9),
  optimal_trees = 0,               # a place to dump results
  min_log_lik = 0                     # a place to dump results
)

nrow(hyper_grid)
```
Iteration through the grid search:
```{r}
# grid search
system.time(for(i in 1:nrow(hyper_grid)) {

  # create parameter list
  params <- list(
    eta = hyper_grid$eta[i],
    max_depth = hyper_grid$max_depth[i],
    min_child_weight = hyper_grid$min_child_weight[i],
    subsample = hyper_grid$subsample[i],
    colsample_bytree = hyper_grid$colsample_bytree[i]
  )

  # reproducibility
  set.seed(123)

  # train model
  xgb.tune <- xgb.cv(
    params = params,
    data = features_train,
    label = response_train,
    nrounds = 500,
    nfold = 5,
    objective = "reg:gamma",  # for regression models
    tree_method = "hist",
    verbose = 0,               # silent,
    early_stopping_rounds = 10 # stop if no improvement for 10 consecutive trees
  )

  # add min training error and trees to grid
  hyper_grid$optimal_trees[i] <- which.min(xgb.tune$evaluation_log$test_gamma_nloglik_mean)
  hyper_grid$log_lik[i] <- min(xgb.tune$evaluation_log$test_gamma_nloglik_mean)
})

```

Results
```{r}
# Results
hyper_grid %>%
  dplyr::arrange(log_lik) %>%
  head(10)
```

### Run the model with the optimal parameters
We run the model based on the parameters from the experiment above.
```{r}
#########################
# Run the optimal model #
#########################

# Use the xgb.DMatrix to format the data

# Remove the ClaimNb from the data
df_train2 <- subset(df_train, select = -c(ClaimAmount, ClaimNb))
#glimpse(df_train2)
#glimpse(df_train)

# Formating the data
dtrain <- xgb.DMatrix(data = data.matrix(df_train2), label = df_train$ClaimAmount/df_train$ClaimNb, weight=df_train$Exposure)
#glimpse(dtrain)

# create parameter list
params_list3 <- list(
  eta = .05,
  max_depth = 1, # choice a stump tree
  min_child_weight = 1,
  subsample = .65,
  colsample_bytree = .8
)

# Fit the model with the obtained parameters
system.time(xgb.fit.sev.bis <- xgboost(
  data = features_train,
  label = response_train, #number claims / exposure
  params = params_list3,
  nrounds = 240,# number of trees
  objective = "reg:gamma",  # for countinf model
  tree_method = "hist",
  verbose = 0               # silent,
))

```

### Visuals

Here we focus on the Gain, which stands for the relative contribution of the corresponding feature to the model calculated by taking each feature’s contribution for each tree in the model.
```{r}
# create importance matrix
importance_matrix <- xgb.importance(model = xgb.fit.sev.bis)
print(importance_matrix)

# variable importance plot
xgb.plot.importance(importance_matrix, top_n = 10, measure = "Gain")
#?xgb.plot.importance

# Save the model
xgb.save(xgb.fit.sev.bis, "xgbm_Claims_sev")
```
#### Variable Importance Plot (VIP)
```{r}
xgb.plot.importance(importance_matrix, top_n = 10, measure = "Frequency")
```

```{r}
xgb.plot.importance(importance_matrix, top_n = 10, measure = "Cover")
```

```{r}
#install.packages("DiagrammeR")
library(DiagrammeR)
xgb.plot.tree(feature_names = colnames(features_train),
              model = xgb.fit.sev.bis,
              trees = 0)

# ?interaction.plot
# interaction.plot(train.comb.cxl$MileBand,train.comb.cxl$TermBand,train.comb.cxl$ClaimCnt,sum)

# Partial Dependance Plot (PDP)
```

```{r}
# Better to use them with Continuous variable
pdp <- xgb.fit.sev.bis %>%
  pdp::partial(pred.var = "DriverAge", n.trees = 500, grid.resolution = 100, train = features_train) %>%
  autoplot(rug = TRUE, train = features_train) +
  scale_y_continuous(labels = scales::dollar) +
  ggtitle("PDP")

#print(pdp)

ice <- xgb.fit.sev.bis %>%
  pdp::partial(pred.var = "DriverAge", n.trees = 500, grid.resolution = 100, train = features_train, ice = TRUE) %>%
  autoplot(rug = TRUE, train = features_train, alpha = .1, center = TRUE) +
  scale_y_continuous(labels = scales::dollar) +
  ggtitle("ICE")

#plot(ice)

gridExtra::grid.arrange(pdp, ice, nrow = 1)
```
